---
title: "DataHw1-Qn2"
author: "Charls Joseph"
date: "March 26, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the 'junk1.txt' file.

There are 100 observation with 3 columns.

```{r}
library(VIM)

df <- read.csv("C:\\Users\\Charls\\Documents\\CunyMSDS\\Data622\\Assignments\\HW1\\Qn2\\junk1.txt", header = T, sep = ' ')
dim(df)

```

## EDA for dataset 'junk1.txt"

The given dataset is balanced(i.e both classes are evenly distributed.)
a is a numeric value ranges from -2.2 to 3 
b is a numeric value ranges from -3.1 to 3
class - 1, 2 

Note: Need to know the metadata for this dataset

```{r}
table(df$class)

summary(df)

```

Using boxplot, determine whether there is any outliers. No outliers are found. 

```{r}
boxplot(df)

```

Using aggr plot, we dont see any missing values.


```{r}
aggr_plot <- aggr(df, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(df), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))

```

## Load the 'junk2.csv' file.

There are 4000 Observations with 3 columns.

```{r}


df1 <- read.csv("C:\\Users\\Charls\\Documents\\CunyMSDS\\Data622\\Assignments\\HW1\\Qn2\\junk2.csv", header = T, sep = ',')

dim(df1)


```

The given dataset is imbalanced(i.e both classes are not evenly distributed.)
a is a numeric value ranges from -4.1 to 4.6 
b is a numeric value ranges from -3.9 to 4.31
class - 0, 1 

Note: 
1. Need to know the metadata for this dataset. What are variable a, b and class in business terms.

2. It would be great if we can get a balanced dataset if possible. 

3. Assuming that the given dataset is based on a normal distribution, the response variable is always imbalanced. So I would ask business which performance metrics i should try to improve. Whether it is Type1 error/Precision or type2/Recall while evalvating the model performance. This is very crucial for determining the optimal value of threshold for classification. 


```{r}

table(df1$class)

summary(df1)

```

Using boxplots, we are seeing some outliers for both a, b variable. Extract those and ask business team that they are all genuine and determine the need of removing it from the dataset. 


```{r}
boxplot(df1)
```

There is no missing values
```{r}

aggr_plot <- aggr(df1, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(df1), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))

```